Data Preparation

### 2019-01-09 Data Preparation.Rmd
adding libraries used in transcripts.
imports grade data

library(gsheet) # import spreadsheets from google drive
library(tm)
library(hunspell) # Stemmer
```

@@

@@

```
# Save Data

>>>>

library(gsheet) # import spreadsheets from google drive
library(tm)
library(hunspell) # Stemmer

library(rlist)
#library(tidyr) #(maybe incuded in tidyverse)
#library(tibble)
```

@@

ALL OTHER STUDENTS:
The data we will be using was provided in two documents with the same format. We import them, merge them and remove duplicate rows.

```{r Data Import}
t1 <- read.csv("Raw Grades/grades1.csv",na.strings=c("","NA"))
t2 <- read.csv("Raw Grades/grades2.csv",na.strings=c("","NA"))
d_dirt <-rbind(t1, t2)
d_dirt <- d_dirt[!duplicated(d_dirt),] #could use distinct() from dplyr
```

@@

# Save Data
